---
title: "Regression models course project"
author: "Maurizio Murino"
date: "25 February 2016"
output: word_document
---

#1. Introduction

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG”
"Quantify the MPG difference between automatic and manual transmissions"

#2. Exploration

`mtcars` counts 32 observations on 11 variables. pairs() allows us to sketch a rapid idea of the relations between the variables that we would like to explore in the second part of the analysis.

```{r exploration 1}
pairs(mtcars)
```

Operativelly, we explore the relationship between miles-per-gallon (MPG) and other variables in the `mtcars` data set. 

```{r exploration 2}
dim(mtcars)
str(mtcars)
summary(mtcars)
```

#3. Analysis

As told before, we focus on the relationship between `mpg` (Miles/(US) gallon) and `am` (Transmission). 

```{r analysis 1}
data(mtcars)
boxplot(mpg ~ am, data = mtcars, xlab = "Transmission (0 = automatic, 1 = manual)", main = "Miles/gallon per transmission")
```

Manual transmission has, in appearance, a role in favorably increase the average vehicle consumption.

To have a further confirm, we have to have an idea of the other predictors of the dataset. An ANOVA model can turn in use.

```{r analysis 2}
anova1 <- aov(mpg ~ ., data = mtcars)
summary(anova1)
```

Because of the low p-value (below 0.05), we will consider the variables `cyl`, `disp`, `wt`, `drat`, `am` as more interesting predictor variables.

```{r analysis 3}
lm1 <- lm(mpg ~ cyl + disp + wt + drat + am, data = mtcars)
summary(lm1)
```

`drat` and `disp` has a really high coefficient, they could be of some disturb. We try to make the approach more precise by cutting uit from the model.

```{r analysis 4}
lm2 <- lm(mpg ~ cyl + wt + am, data = mtcars)
summary(lm2)
```

The adjusted r-squared is 0.83. We cannot reject the hypothesis that the coefficient of am is 0.

#4. Diagnosis

```{r Diagnosis  1}
par(mfrow = c(2, 2))
plot(lm2)
```

Appearently, there is not a relevant pattern found according to upper left graph. The `normal Q-Q` suggests the model mets the normality assumption. `Scale-Location` shows constant variance assumption are satisfied. We can conclude that weight and number of cylinders play important role to determination of `mpg`.

